QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`

### 2024-03-11 minos/outcomes/QALY_comparison2.Rmd
Removed reweighting of SF12 vars in QALY calculation as it caused problems. Not required for synthpop runs anyway

```{r}
experiment <- params$experiment
baseline <- params$base
intervention <- params$intervention
start.year <- params$start.year
# 
# experiment <- 'default_config'
# baseline <- 'baseline'
# intervention <- '50All'
```

@@

>>>>

```{r}
experiment <- params$experiment
baseline <- params$base
intervention <- params$intervention
start.year <- params$start.year
# # 
# experiment <- 'glasgow_scaled'
# baseline <- 'baseline'
# intervention <- '50All'
# start.year <- 2020
```

@@

# Sample Information
